HPC--101\\Onboarding

### 2016-04-22 hpc_101/paper.tex
added problem reporting and fixed a typo

\section{Cluster Etiquette}
\begin{frame}
\frametitle{Cluster Etiquette}
\begin{itemize}
\item Never run anything on the login nodes
\item Try to request only the resources that your job needs.  Leaving unneeded resources available, allows other users to use them
\item Test what your application in an interactive session before scheduling a long running job
\begin{itemize}
\item[--] This can help identify what resources your job will require, and potentially aid you in correctly sizing what resources you request.
\end{itemize}
\item Use the nodes in the sb.q to validate your slurm script runs as intended
\begin{itemize}
\item[--] This helps to reduce the chance of you having a small error that kills your job prematurely after waiting for resources 
\end{itemize} 
\item Always run jobs from within {\ctilde}/lus/ directory to ensure output is written there and does not fill up the system filesystem
\end{itemize}
\end{frame}

>>>>

\section{Problem Reporting}
\begin{frame}
\frametitle{Problem Reporting}
\begin{itemize}
\item Always email UH-HPC-Help@lists.hawaii.edu
\item For batch jobs...
\begin{itemize}
\item[--] Job ID, path to submission script, submission command, error file location, output files
\end{itemize} 
\item For other problems...
\begin{itemize}
\item[--] State the problem, command issued, host, directory, remote host, error messages
\end{itemize}
\end{itemize}
\end{frame}

\section{Cluster Etiquette}
\begin{frame}
\frametitle{Cluster Etiquette}
\begin{itemize}
\item Never run anything on the login nodes
\item Try to request only the resources that your job needs.  Leaving unneeded resources available, allows other users to use them
\item Test your application in an interactive session before scheduling a long running job
\begin{itemize}
\item[--] This can help identify what resources your job will require, and potentially aid you in correctly sizing what resources you request.
\end{itemize}
\item Use the nodes in the sb.q to validate your slurm script runs as intended
\begin{itemize}
\item[--] This helps to reduce the chance of you having a small error that kills your job prematurely after waiting for resources 
\end{itemize} 
\item Always run jobs from within {\ctilde}/lus/ directory to ensure output is written there and does not fill up the system filesystem
\end{itemize}
\end{frame}
